### 2015-03-08 docs/report/inlining.tex

\note{The serial works with a \code{Uint8ClampedArray} but accesses three elements at the same time. The parallel implementation uses a \code{Uint32Array} and works on one pixel (A,R,G,B) at a time.}

@@

\subsection{The problem}
Taking the experience from previous experiments into account we considered that the performance of the two implementation with a \code{Uint32Array} of about \(8E7\) (eight million) elements should be similar, even favoring the parallel one. The initial measurements showed that the linear implementation fared approximately four times better than the parallel one.

@@

\subsubsection{Serial implementation generated code}
Figures \ref{fig:parallel-clamp} through \ref{fig:parallel-noise} are related to the serial implementation. As it can be seen from them, only \code{Math.random} is being inlined.
\img{\code{clamp} function - parallel implementation}{../../spikes/3.1.3/irhydra-pjs-noinlined/ww-clamp}{fig:parallel-clamp}
\img{\code{colorDistance} function - parallel implementation}{../../spikes/3.1.3/irhydra-pjs-noinlined/ww-colorDistance}{fig:parallel-colorDistance}
\img{\code{mapper} function - parallel implementation}{../../spikes/3.1.3/irhydra-pjs-noinlined/ww-mapper}{fig:parallel-mapper}
\img{\code{noise} function - parallel implementation}{../../spikes/3.1.3/irhydra-pjs-noinlined/ww-noise}{fig:parallel-noise}

>>>>

\note{The serial code works with a \code{Uint8ClampedArray} but accesses three elements at the same time. The parallel implementation uses a \code{Uint32Array} and works on one pixel (A,R,G,B) at a time.}

@@

\subsection{The problem}
Taking the experience from previous experiments into account we considered that the performance of the two implementations with a source \code{Uint32Array} of about \(8E7\) (eight million) elements should be similar, even favoring the parallel one. The initial measurements showed that the linear implementation fared approximately four times better than the parallel one.

@@

\subsubsection{Parallel implementation generated code}
Figures \ref{fig:parallel-clamp} through \ref{fig:parallel-noise} are related to the serial implementation. As it can be seen from them, only \code{Math.random} is being inlined.
\img{\code{clamp} function - parallel implementation}{../../spikes/3.1.3/irhydra-pjs-noinlined/ww-clamp}{fig:parallel-clamp}
\img{\code{colorDistance} function - parallel implementation}{../../spikes/3.1.3/irhydra-pjs-noinlined/ww-colorDistance}{fig:parallel-colorDistance}
\img{\code{mapper} function - parallel implementation}{../../spikes/3.1.3/irhydra-pjs-noinlined/ww-mapper}{fig:parallel-mapper}
\img{\code{noise} function - parallel implementation}{../../spikes/3.1.3/irhydra-pjs-noinlined/ww-noise}{fig:parallel-noise}
